Key Derivation From Noisy Sources With More Errors Than Entropy

### 2014-09-22 constantRate/ConstCompFuzzExt-reorg.tex
adding blinding command

\documentclass[11pt]{article}
%\documentclass{llncs}
\def\shownotes{1}

@@

\ifnum\shownotes=1
\newcommand{\authnote}[2]{{\textcolor{red}{\textsf{#1 notes: }\textcolor{blue}{ #2}}\marginpar{\textcolor{red}{\textbf{!!!!!}}}}}
\else
\newcommand{\authnote}[2]{}
\fi
\newcommand{\bnote}[1]{{\authnote{Ben}{#1}}}
\newcommand{\lnote}[1]{{\authnote{Leo}{#1}}}
\newcommand{\rnote}[1]{{\authnote{Ran}{#1}}}
\newcommand{\onote}[1]{{\authnote{Omer}{#1}}}

@@

\title{Key Derivation From Noisy Sources With More Errors Than Entropy}
%\author{Ran Canetti \and Benjamin Fuller\footnote{The Lincoln Laboratory portion of this
%work was sponsored by the Department of the Air Force under Air Force
%Contract
%\#FA8721-05-C-0002.  Opinions,
%interpretations, conclusions and recommendations are those of the author
%and
%are not necessarily endorsed by the United States Government.} \and Omer Paneth \and Leonid Reyzin \and Adam Smith}

\begin{document}
\maketitle

@@

In this work, we exploit source structure to construct fuzzy extractors for large classes of sources with more errors than entropy.  Our constructions are for the Hamming metric over symbols of some alphabet $\mathcal{Z}$.  We present both information-theoretic and computational constructions.

@@

\bibliographystyle{alpha}
\bibliography{crypto}

>>>>

\documentclass[11pt]{article}
%\documentclass{llncs}
\def\shownotes{1}
\def\blinded{0}

@@

\ifnum\blinded=0
\newcommand{\blind}[1]{{#1}}
\else
\newcommand{\blind}[1]{}
\def\shownotes{0}
\fi

\ifnum\shownotes=1
\newcommand{\authnote}[2]{{\textcolor{red}{\textsf{#1 notes: }\textcolor{blue}{ #2}}\marginpar{\textcolor{red}{\textbf{!!!!!}}}}}
\else
\newcommand{\authnote}[2]{}
\fi

\newcommand{\bnote}[1]{{\authnote{Ben}{#1}}}
\newcommand{\lnote}[1]{{\authnote{Leo}{#1}}}
\newcommand{\rnote}[1]{{\authnote{Ran}{#1}}}
\newcommand{\onote}[1]{{\authnote{Omer}{#1}}}

@@

\title{Key Derivation From Noisy Sources With More Errors Than Entropy}
%\author{Ran Canetti \and Benjamin Fuller \and Omer Paneth \and Leonid Reyzin \and Adam Smith}
\blind{
\author{Ran Canetti\footnote{Email: {\tt canetti@cs.bu.edu}. Boston University and Tel Aviv University.} \and Benjamin Fuller\footnote{Email: {\tt bfuller@cs.bu.edu}.  Boston University and MIT Lincoln Laboratory.} \and Omer Paneth\footnote{Email: {\tt paneth@cs.bu.edu}. Boston University.} \and Leonid Reyzin\footnote{Email: {\tt reyzin@cs.bu.edu}.  Boston University.} \and Adam Smith\footnote{Email: {\tt asmith@cse.psu.edu}.  Pennsylvania State University.} }
}
\begin{document}
\maketitle

@@

In this work, we exploit source structure to construct fuzzy extractors for large classes of sources with more errors than entropy.  Our constructions are for the Hamming metric over symbols of some alphabet .  We present both information-theoretic and computational constructions.

@@

\blind{
\section*{Acknowledgements}
The authors are grateful to Nishanth Chandran, Sharon Goldberg, Gene Itkis, Bhavana Kanukurthi, and Mayank Varia for helpful discussions, creative ideas, and important references.

This work is supported in part by National Science Foundation grants 0831281, 1012910, 1012798, and 1218461. 
Omer Paneth is additionally supported by the Simons award for graduate students in theoretical computer science.
The work of Benjamin Fuller is sponsored in part by the United States Air Force under Air Force Contract FA8721-05-C-0002. Opinions, interpretations, conclusions and recommendations are those of the authors and are not necessarily endorsed by the United States Government.
}
\bibliographystyle{alpha}
\bibliography{crypto}
